---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# glm.deploy

Generates the source code of the scoring algorithm (predict) of a GLM object to C or JAVA to deploy/operationalize it outside R.

#Output options
At this stage output source code availables are: C and Java.

#Link Function Compatibility
The link functions compatible are: identity, probit, cloglog, log, sqrt, inverse, 1/mu^2, logit

## Example

This is a basic example with the iris dataset to create a glm object and pass it to the two functions glm2c and glm2java:

```{r example}
## basic example code
  data(iris)
  iristest = iris
  iristest$Virginica = ifelse(iristest$Species == 'virginica', TRUE,FALSE)
  iristest$Species = NULL
  model <- glm(Virginica ~ ., family = binomial(logit), data=iristest)
  glm2c(model)
  glm2java(model)
```

## Author

Oscar J. Castro-Lopez, Ines F. Vega-Lopez
